6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Stuff

Testing is an extremely important part of the software development lifecycle, and is key to delivering a quality product. The system I have developed composes a number of interconnected components, each of which must be tested in isolation and as a whole to ensure correctness.

@@

Unit Testing is a simple and effective way of ensuring units of functionality such as classes and methods behave correctly. Unit testing can be used to pinpoint the exact cause of a problem, as the code tested is isolated as well as possible from other interacting components such as databases. Running tests frequently during development provides a fast feedback loop in which correctness of new code can be verified, as well as detecting regressions in other areas of the code.

@@

The management agent in particular benefited from this form of testing. The DSL uses a number of meta-programming capabilities of Ruby, discussed in a previous section. The meta-programming features can, in some cases, make it harder to reason about the implementation code. A suite of unit tests specifically for the parsing of the DSL were both simple to write and extremely valuable in improving its quality and correctness.

The small amount of configuration within the event streaming service was unit tested. As Riemann itself is a well tested event processing library, there was no need to test its functionality too. Therefore there are only a couple of test cases needed for this component.

@@

While unit testing can be very beneficial in improving the quality of individual components, it does not expose any defects relating to the integration of these components into the whole system. Functional, or integration tests can vary from the combination of two components to testing the entire system end-to-end.

They can typically be automated in the same way as unit tests, but it is generally more challenging and time consuming to do so. They can expose a large number of more subtle defects which are much more difficult to find after the software has been deployed.

@@

The following functional tests were carried out, as they correspond to an important piece of functionality that is not possible to verify via unit tests:

@@

Positive findings of real world usage testing:

\begin{itemize}
  \item It was simple to write a basic set of tests for an existing service.
  \item The service discovery feature was simple and effective, and provided a usable service specification template to build upon.
  \item After the initial setup, it became obvious that the tool could be used to detect some subtle problems, such as missing nightly database backups.
\end{itemize}

@@

\pagebreak
\section{Critical Evaluation}

As evident from the previous subsections, the system delivered at least partially satisfied every requirement set out in the analysis phase. The tool is practically usable and deployed on a number of real systems. There are however a few weaknesses or areas of improvement upon the final implementation:

>>>>

Testing is an extremely important part of the software development lifecycle, and is key to delivering a quality product. The system I have developed composes a number of interconnected components, each of which must be tested in isolation and as a whole, to ensure correctness.

@@

Unit Testing is a simple and effective way of ensuring units of functionality such as classes and methods behave correctly. Unit testing can be used to pinpoint the exact cause of a problem, as the code tested is isolated as well as possible from other interacting components such as databases. Running tests frequently during development provides a fast feedback loop in which correctness of new code can be verified, as well as detecting unexpected regressions in other areas of the code.

@@

The management agent in particular benefited from this form of testing. The DSL uses a number of meta-programming capabilities of Ruby, discussed in a previous section. The meta-programming features can, in some cases, make it harder to reason about the correctness of the implementation. A suite of unit tests specifically for the parsing of the DSL were both simple to write and extremely valuable in improving its quality and correctness.

The small amount of configuration within the event streaming service was also unit tested. As Riemann itself is a well tested event processing library, there was no need to test its functionality too. Therefore there are only a couple of test cases needed for this component.

@@

While unit testing can be very beneficial in improving the quality of individual components, it does not expose any defects relating to the integration of these components into the whole system. Functional tests can vary from the combination of two components to testing the entire system end-to-end in order to validate if requirements have been satisfied.

Functional tests can typically be automated in the same way as unit tests, but it is generally more challenging and time consuming to do so. They can expose a large number of more subtle defects which are much more difficult to find after the software has been deployed.

@@

Below are examples of the functional tests carried out, as they correspond to an important piece of functionality that is not possible to verify via unit tests:

@@

Some positive findings from real world usage testing include:

\begin{itemize}
  \item It was simple to write a basic set of tests for an existing service.
  \item The produced architecture diagrams were invaluable in checking the accuracy of a service specification, as well as communicating this to others.
  \item The service discovery feature was simple and effective, and provided a usable service specification template to build upon.
  \item After the initial setup, it became obvious that the tool could be used to detect some subtle problems, such as missing nightly database backups.
\end{itemize}

@@

\section{Critical Evaluation}

As evident from the previous subsections, the system delivered at least partially satisfied every requirement set out in the analysis phase, in that regard it can be considered successful. The tool is practically usable and deployed on a number of real systems. Areas where particular improvements have been made upon previous tools are noted below:

\begin{description}
  \item[Check Flexibility] The ability to check arbitrary properties of a system from a black box perspective (without access to the source code) can be seen as a significant benefit of using this tool.
  \item[Effective Visualization \& Communication] Perhaps the largest improvement over existing monitoring tools such as Nagios is the quality of visualization. Service specifications generate easy to understand architecture diagrams of dependencies, with live updates when the state of each component changes. The extra context that this provides means that operations teams will be better placed to understand the modelled systems and the impact of problems whenever they occur.
  \item[Root Cause Analysis] Whilst the root cause analysis mechanism is quite simple, it has proven to be effective in narrowing down the scope of problems, especially in more complex systems and therefore aiding in their resolution. Most other monitoring tools lack the context to be able to do this kind of analysis.
\end{description}

There are however a few weaknesses or areas of improvement upon the final implementation:
